\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-20 Manuscript/manuscript.tex
requested a figure on fitted density
responded to Prof. Yan's to do list

\jy{Owen, please prepare the following:
1) A table of the model parameter estimates (both point estimate and
standard error). This is similar to the current table, with and
without 2022 data. Let's focus on model gg3b and leave the model
comparison results in the supplement.
2) Figure: random effects at the venue level with/without 2022
data. Similar to the current figure.
3) Diagnostic plots: qq-plot for the gg3b model. QQ-plot for the
normal random effects could be placed in supplement.
4) Table: assessing the 0.1 threshold, similar to the current table.
I'll take care of the writing when you get the results.}

\begin{table}
  \centering
  \caption{AIC and estimated parameters for the three models fitted to the
    data.}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c c}
    \toprule
    Data set & Model & AIC & $\sigma_h$ & $\sigma_v$ & $\alpha$ & $\sqrt{\phi}$ \\
    \midrule
    Excluding 2022 &
      Venue Effect Only & $-1862.2$ &   & 0.048 & $-1.857$ & 0.152\\
     & Heat Effect Only & $-1910.9$ & 0.069 &  & $-1.877$ & 0.136\\
     & Venue and Heat Effect & $-1912.9$ & 0.058 & 0.033 & $-1.868$ & 0.136\\[1ex]
    Including 2022 &
    Venue Effect Only & $-3798.8$ &   & 0.054 & $-1.871$ & 0.149\\
    & Heat Effect Only & $-2070.7$ & 0.073 &  & $-1.890$ & 0.135\\
    & Venue and Heat Effect & $-2075.7$ & 0.057 & 0.040 & $-1.881$ & 0.134\\
    \bottomrule
  \end{tabular}
\end{table}
\of{needs to be updated with current values. But I did start to alter something
then stopped.}

@@

@@

@@

\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than threshold 0.08,
  0.09, and 0.10 seconds based on the two effect model.}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & Threshold 0.08 & Threshold 0.09 & Threshold 0.10  \\ 
   \midrule
   Excluding 2022 & $1.10\cdot10^{-5}$ & $2.34\cdot10^{-4}$ &  $2.36\cdot10^{-3}$  \\ 
   Including 2022 & $1.71\cdot10^{-5}$ & $3.01\cdot10^{-4}$ & $2.90\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}
\of{table has been updated}

@@

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on tail probabilities.}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & Tail probability  $10^{-3}$ & Tail probability $10^{-4}$ \\ 
   \midrule
   Excluding 2022 & $0.096$ & $0.087$ \\ 
   Including 2022 & $0.095$ & $0.086$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time}
\end{table}
\of{table has been updated}

>>>>

\jy{Owen, please prepare the following:
1) A table of the model parameter estimates (both point estimate and
standard error). This is similar to the current table, with and
without 2022 data. Let's focus on model gg3b and leave the model
comparison results in the supplement.
2) Figure: random effects at the venue level with/without 2022
data. Similar to the current figure.
3) Diagnostic plots: qq-plot for the gg3b model. QQ-plot for the
normal random effects could be placed in supplement.
4) Table: assessing the 0.1 threshold, similar to the current table.
I'll take care of the writing when you get the results.}
\of{1) Is resolved in table 2, 2) is resolved in figure 4, 3) is resolved in
figure 3. 4) is resolved in tables 3 and 4.}

\jy{Owen: an additional figure of the GG density without random
  effects (use \texttt{curve(dGG(x, mu = , sigma = , nu =  ), 0, 0.03)}) and
  with random effects (through \texttt{density()})}
\of{Please see figure 5}

\begin{table}
  \centering
  \caption{AIC and estimated parameters for the gg3b model fit}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c c}
    \toprule
    Data set & AIC & $\mu$ & $\sigma$ & $\nu$ & $\sigma_v$ & $\sigma_h$ \\
    \midrule
    Excluding 2022 & -3660 & -1.900 & -2.192 & -1.315 & 0.0434 & 0.3259 \\
    Including 2022 & -4103 & -1.910 & -2.200 & -1.178 & 0.0576 & 0.3198 \\
    \bottomrule
  \end{tabular}
\end{table}
\of{Created these with the function I wrote model-name at bottom of gamlss.R. Do
any other parametes need to be added?}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{GGResiduals}
  \caption{Residuals from the GG model}
  \label{fig:Residuals}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{GGDensity}
  \caption{The densities of the GG distribution with random effects for heat
  and venue (black), and without random effects (blue)}
  \label{fig:DensityPlot}
\end{figure}

@@

\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than threshold 0.08,
  0.09, and 0.10 seconds based on the two effect model.}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & Threshold 0.08 & Threshold 0.09 & Threshold 0.10  \\ 
   \midrule
   Excluding 2022 & $5.31\cdot10^{-5}$ & $3.53\cdot10^{-4}$ &  $1.94\cdot10^{-3}$  \\ 
   Including 2022 & $6.84\cdot10^{-5}$ & $4.95\cdot10^{-4}$ & $2.76\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}
\of{table has been updated with gg3b results}

@@

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on tail probabilities.}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & Tail probability  $10^{-3}$ & Tail probability $10^{-4}$ \\ 
   \midrule
   Excluding 2022 & $0.096$ & $0.083$ \\ 
   Including 2022 & $0.094$ & $0.082$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time}
\end{table}
\of{table has been updated with gg3b results}
